Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-09 main.tex
rough draft for second part of intro (WIP)

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, varying memory sizes make it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}, which acts as proxy for the total execution time of a
    workflow.

    \begin{itemize}
      \item HEFT (see book chapter) is one of the most popular heuristics (cite a review).
      \item However, existing HEFT variations do not take memory sizes into consideration (\skug{check in related work if true!}).
        Note: 2 papers that deal with memory sizes, but model is very different!
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

@@

    \section{Related work: \skug{Full: 5, Polished: 4}}

>>>>

    %%% MOTIVATION %%%
    Modern computing platforms are often heterogeneous, meaning they feature varying CPU speeds
    and memory sizes. In general, varying memory sizes make it more challenging to compute
    a schedule that respects all memory constraints -- meaning that no task is executed on a 
    processor with less memory than needed for the task. This is, however, very important to
    avoid (possibly expensive) runtime failures and to provide a satisfactory user experience.
    Hence, building on previous related work~\cite{TODO}, we consider a scheduling problem 
    formulation that takes memory sizes as explicit constraints into account. Its objective is
    the very common \emph{makespan}~\cite{liu2018survey}, 
    which acts as proxy for the total execution time of a workflow.

    A seminal list-based scheduling heuristic for workflows is HEFT 
    (heterogeneous earliest finish time)~\cite{topcuoglu2002performance}.
    It has two phases: (i) each task is assigned a priority and (ii) the tasks are assigned
    to processors, where the ``ready'' task with the highest priority is scheduled next.
    HEFT has been extended (e.g.\ by Shi and Dongarra~\cite{SHI2006665}) and adjusted for a variety of different scheduling problem formulations. 
    Yet, none of them adheres to memory constraints -- also see our discussion of related work
    in Section~\ref{sec:related-work}. (\skug{check in related work if true!}).
        \skug{Note: 2 papers that deal with memory sizes, but model is very different!}

    \begin{itemize}
      \item Many scheduling strategies assume that task running times provided to them are accurate. This is not really the case
        in practice. Thus, one needs to adapt the schedule when major deviations occur (which is the case in practice).
        List-based schedulers such as HEFT are not designed for adaptation and would compute a completely schedule from scratch.
    \end{itemize}

@@

    \section{Related work: \skug{Full: 5, Polished: 4}}
    \label{sec:related-work}

    \hmey{Question: Does it make sense to place related work before the model (which is more common)?}
